\bf Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-10 acl.2016/amta2016.tex
whatever

\section{Other Models and Even More Cores}

@@

>>>>

\subsection{Other Models and Even More Cores}

@@

\subsection{Translation Quality}

Our work is intended as a drop-in replacement for the Moses decoder. Given the same parameters and models, the model scores are comparable and the search space should be identical (or very nearly identical). This should lead to almost translation quality, which we verify with Figure~\ref{???}.
